---
title: "Assignment 1"
author: "Pavan Kumar Mekala"
date: "2024-02-04"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 2 Importing Dataset into R
```{r Importing Dataset}
Dailyactivities <- read.csv("ss.csv")


```
## Imported data set from the website Kaggle.com by using the below link
## https://www.kaggle.com/datasets/henryshan/sleep-health-and-lifestyle

## 3 Print out descriptive statistics for a selection of quantitative and categorical variables

```{r Descriptive Statistics}
summary(Dailyactivities)
head(Dailyactivities,n=10)
tail(Dailyactivities,n=10)
nrow(Dailyactivities)
ncol(Dailyactivities)


```
## Printed descriptive statistics for a selection of quantitative and categorical variables and checked summary, head, tail, number of rows, number of columns by using summary, head, tail, nrow, ncol functions
 
## 4 Transform at least one variable
```{r Transform at least one variable}
Daily.Steps_per_hour <- Dailyactivities$Daily.Steps /24
Daily.Steps_per_hour
```
## Transformed the variable Dailyactivities$Daily.steps by dividing with 24 to measure the Daily.steps happening per hour and stored in Daily.Steps_per_hour

## 5.1 Plot at least one quantitative variable
```{r Plot at least one quatitative variable}
hist(Dailyactivities$Quality.of.Sleep)

```
## Plotted the histogram of Dailyactivities$Quality.of.Sleep

## 5.2 Scatter Plot
```{r Scatter Plot}
x=Dailyactivities$Stress.Level
y=Dailyactivities$Age
plot(x,y)

```
## Scatter plotted between Dailyactivities$Stress.level and Dailyactivities$Age by taking Dailyactivities$Stess.level on X and Dailyactivities$Age on Y
